Methodology for Assessing the State of the Practice for Domain X

### 2020-08-31 StateOfPractice/Methodology/Methodology.tex
updated 'Initially Filter the Software List' in Methodology document

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be completed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be completed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be completed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be completed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed}
\item Measure using ``shallow'' measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be completed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be completed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item With short list:
\begin{enumerate}
\item Survey developers \pmi{To do: Link to survey}
\item Usability experiments \pmi{Move the below usability section to a new doc, and link to it.}
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

@@

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
\pmi{outline here how to find such a list}
\begin{enumerate}
\item Must have viewable source code.
\item Ideally have a git repository. \pmi{Not all of mine had this..}
\end{enumerate}

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The person doing this must keep track of both the initial and filtered lists. The reasons for this is traceability bc..
\begin{enumerate}
	\item Professionalism..
	\item Available documentation..
	\item Status..
	\item Availability of source code..
\end{enumerate}

>>>>

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be reviewed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be completed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed}
\item Measure using ``shallow'' measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be completed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be completed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item With short list:
\begin{enumerate}
\item Survey developers \pmi{To do: Link to survey}
\item Usability experiments \pmi{Move the below usability section to a new doc, and link to it.}
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

@@

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
The candidate software can be found through search engine queries and domain related publications. The candidate software should have the following properties:
\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather emprical measures found in Section \ref{SecEmpiricalMeasures}.
\end{enumerate}

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The initial list of candidate software should be filtered using the following properties:
\begin{enumerate}
	\item Organization - The software and any related documentation should appear to be easy to gather and understand.
	\item Available documentation - The purpose of the software and the installation and usage procedures should appear to be moderately clear or easy to find.
	\item Status - The software cannot be marked as incomplete or in an initial development phase.
\end{enumerate}

Copies of both the initial and filtered lists should be kept for traceability purposes.
